Object Categorization based on RGBD data

### 2014-01-03 Disseration/introduction.tex
aa

	Capturing visual information have never been easier. Terabytes of photographs and movies are uploaded on the Web every day, causing unprecedented growth of popular storage services. The traditional means of annotation cease to suffice. Hand-tagging and description have strong cultural dependencies and introduce ambiguity. Without any better solution, databases become increasingly harder to navigate and browse. Matters could have been better if computers understood content they deal with. But even the latest software is far from and cannot be considered intelligent in general terms. On the other hand, an area of machine learning define routines for learning complex and strongly non-linear functions mapping an arbitrary input to a given set of outputs. This is how computer vision can be used to make sense of any visual content, provided that there is enough data. As Forsyth and Ponce \cite{ponce2011cv} have it:

@@

	How about semantic classification of scenes or objects? Suppose a mobile robot would know, or understand, what does it have to deal with. Suppose a robot would know that it is about to take, say, a glass of water. How would it affect the robot's behaviour? Could it have any impact on the force of the grip? or the speed and the manner of the planned object movement? Answers for all this questions are yes. Semantic classification is possible, but it requires clever mechanisms of computer vision and powerful computers. It can be seen as a part of a more general classification problem, which machine learning handles quite well. Suitable algorithms include, but are not limited to, artificial neural networks, deep belief networks, logistic regression, support vector machines and approaches based on probabilistic graphical models. One has to bear in mind that none of them can handle the problem directly. That is, it is inconceivable to feed a whole image as is into a classifier --- some degree of preprocessing is required. One such preprocessing technique is translation of image into a feature vector. What should this vector comprise of? A Bag of Words model is one technique that answers this question. This model has been first used for scene classification in 2004 in \cite{csurka2004visual} and maintains its popularity ever since.

	In this paper a technique for semantic object classification based on three dimensional point clouds is presented. The rest of this chapter is organised as follows: Section 1 describes the Bag of Words technique in detail. Construction of an image's model is discussed and the most popular algorithms are summarised. Section 2 provides basic information on the problem of classification, introduces basic concepts and methods of classification. Section 3 names C++ computer vision and general purpose libraries used in this project. Finally in Section 4 two datasets of RGBD images are outlined. The following chapters are titled ``Design'' and ``Experiments and Results''. The former contains description of required functionality of a programme for BoW object classification, its design and implementation details. The latter addresses topics of experimental setup, performed experiments and a summary of results.

>>>>

	It has never been easier to capture visual information. Popular storage services grow lighting fast due to terabytes of photographs and movies we upload every day. The growth is so fast that hand-tagging and description, the traditional means of annotation, cease to suffice. They are ambiguous, emotional and rarely optimal. With no better solution at hand, databases are becoming increasingly harder to browse. Another, but quite similar setting occurs in the field of mobile robotics. A mobile robot is there to interact with its enviornment. If so, it would be desirable for the robot to know what kind of an enviornment it is in. The problem can be treated as a scene or object classification problem, one of the most popular computer vision issues in the last decade. As Forsyth and Ponce \cite{ponce2011cv} have it:

@@

	This paper tackles two issues. Firstly, the Bag of Words approach to image classification is reviewed. The Bag of Words approach for classification has originated from the text document classification domain. The approach makes a strong assumption that word occurance define the meaning of the document. It was first used for image classification in 2004 by Csurka \textit{et al} \cite{csurka2004visual}. Since we cannot simply translate an image to natural language a pipeline that help us achieve this goal is needed. It usually consist of steps such as keypoint detection, feature extraction, vector quantization and, finally, classification.

	Secondly, a configurable and flexible application for point cloud classification is designed and implemented in C++. There are many algorithms suitable for the bag of words pipeline. In order to choose an optimal solution for a specific problem extensive evaluation of the algorithms have to be performed. The process can be greatly simplified by a programme that would be: (1) easily extensible, that is adding new algorithms wold be painless and (2) configurable, with every parameter (and algorithm) adjustable at runtime.

       \section{scope and purpose of this work}
       The goal of this work is to design a flexible and configurable application for point cloud classification. The point cloud should be registered by the Microsoft Kinect. The scope of the work is as follows:
       \begin{itemize}
        \item literature review in the area of bag of words image classification
        \item design of a pipeline for bag of words classification of point clouds
        \item design of a configurable programme for point cloud classification
        \item implementation of the programme in C++ using OpenCV and/or PointCloud Library
        \item evaluation of algorithms for bag of words classification
        \item evaluation of the programme on two scientific point cloud databases
       \end{itemize}

	The rest of this chapter is organised as follows: Section 1 describes the Bag of Words technique in detail. Construction of an image's model is discussed and the most popular algorithms are summarised. Section 2 provides basic information on the problem of classification, introduces basic concepts and methods of classification. Section 3 names C++ computer vision and general purpose libraries used in this project. Finally in Section 4 two datasets of RGBD images are outlined. The following chapters are titled ``Design'' and ``Experiments and Results''. The former contains description of required functionality of a programme for BoW object classification, its design and implementation details. The latter addresses topics of experimental setup, performed experiments and a summary of results.
